### 2016-10-31 paper/intro.tex
minor changes to intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up on the
aggregate cost of running a test suite, leading to late reports of test
failures, which can disrupt the development
process~\cite{hilton-etal-ase2016}.  This is often referred to as the
``regression testing problem''.  At large IT companies (e.g.,
Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
common problem .  \Mar{Ask Milos if he can share stories on how
  prevalent regression testing is at Microsoft and Google, if he can
  explain how they run tests, and how prevalent is parallelization (in
  contrast to regression testing).}

@@

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.  We
understand that the alternative of renting server farms (or even
building one) to mitigate the regression testing problem is a
potential escape for large IT organizations but not as attractive for
open-source projects and projects from smaller organizations with
lower budgets for building testing infrastructures.  This paper
studies (1) how relevant the problem of long-running test suites in
open-source software is, (2) what are the causes of high execution
cost (CPU vs. IO), and (3) what is the impact of existing open-source
sound approaches to reducing cost.

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up to the
aggregate cost of running a test suite, leading to late reports of test
failures, which can disrupt the development
process~\cite{hilton-etal-ase2016}.\Comment{  This is often referred to as the
``regression testing problem''.}  At large IT companies (e.g.,
Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
common problem .  \Mar{Ask Milos if he can share stories on how
  prevalent regression testing is at Microsoft and Google, if he can
  explain how they run tests, and how prevalent is parallelization (in
  contrast to regression testing).}

@@

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.
For large IT organizations, the alternative of renting server farms,
or even building one, is a potential escape to mitigate the regression
testing problem.  However, for open-source projects and projects from
smaller organizations with lower budgets for building testing
infrastructures, this alternative is not as attractive.  This paper
studies (1) how relevant the problem of long-running test suites in
open-source software is, (2) what are the causes of high execution
cost (CPU vs. IO), and (3) what is the impact of existing open-source
sound approaches to reducing cost.
